TBD

### 2021-03-13 outputs/paper/paper.Rmd
123

```{r regression, echo=FALSE, warning=FALSE, fig.width=8, fig.height=7}

@@

model <- lm(post_favor_Warren ~., data =FS )
summary(model)

>>>>

```{r regression, echo=FALSE, warning=FALSE, fig.width=10, fig.height=4}

@@

model <- lm(post_favor_Warren ~., data =FS )

## stargazer package to show table results
#install.packages("array")
library(stargazer)

result<-
  model%>%
  stargazer(
          type="text",
          title = "Multiple linear regression model",
          align=TRUE,
          no.space=TRUE,
          digits=2,
          notes.align = "l",
          style = "default",
          dep.var.labels = c("\\normalsize Elizabeth Warren Feeling Thermometer"),
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          font.size = "footnotesize",
          label = "firststage_feelings",
          omit = "response_wave_ID")
